KidsAIR: exposure model

### 2020-05-04 exposure_models.Rmd
exposure analysis updates

# Select analysis vars
selected_vars <- analysis_data %>% 
  filter(area == "WMT") %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke, home_floors_2level, home_pets_2level,
         chimney_clean_3level, stove_cert, wood_collect_2level,
         moisture_closest_2level, sums_events_sampling_period,
         mean_temp_sampling_period_5, amb_pm_sampling_period_5,
         home_act_smoke_2level, home_act_door_2level, stove_grade_3level) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period)) %>% 
  select(-pm_mean_sampling_period) 
```

@@

hist(selected_vars$pm_mean_sampling_period)

# Check for distribution between vars and missingness - see if there are patterns
## No obvious patterns in the missing data
## Missing covars do not seem to be related to the outcomes
missing_hist <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(moisture_closest_2level), "missing yes", "missing no")) %>% 
  ggplot() +
    geom_bar(aes(log_pm_mean_sampling_period), color = "red") +
    facet_wrap(~missing_var)
missing_hist

@@

Next, use `mice()` to impute the missing data
Assess imputed data for summary stats and convergence
```{r}
# Impute missing data; m = 10 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=5, maxit = 5,
                     method = c("polr", "logreg", "logreg", "logreg", "polr",
                                "polr", "logreg", "logreg", "pmm", "pmm",
                                "pmm", "logreg", "logreg", "polr", "pmm"))

>>>>

# Select analysis vars
selected_vars <- analysis_data %>% 
  #filter(area == "WMT") %>% 
  select(home, area, pm_mean_sampling_period, income_3level, 
         residents_smoke, home_floors_2level, home_pets_2level,
         chimney_clean_3level, stove_cert, wood_collect_2level,
         moisture_closest_2level, sums_events_sampling_period,
         mean_temp_sampling_period_5, amb_pm_sampling_period_5,
         home_act_smoke_2level, home_act_door_2level, stove_grade_3level) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period))  
  #select(-pm_mean_sampling_period) 
```

@@

hist(selected_vars$log_pm_mean_sampling_period)

# Check for distribution between vars and missingness - see if there are patterns
## No obvious patterns in the missing data
## Missing covars do not seem to be related to the outcomes

# Histogram
missing_hist <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(residents_smoke), "missing yes", "missing no")) %>% 
  ggplot() +
    geom_bar(aes(log_pm_mean_sampling_period), color = "red") +
    facet_wrap(~missing_var) +
    theme_minimal()
missing_hist

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(residents_smoke), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary

# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(residents_smoke), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

ak_data <- missing_test %>% 
  filter(area == "AK")

nn_data <- missing_test %>% 
  filter(area == "NN")

wmt_data <- missing_test %>% 
  filter(area == "WMT")

t.test(log_pm_mean_sampling_period ~ missing_var, data = ak_data)
t.test(log_pm_mean_sampling_period ~ missing_var, data = nn_data)
t.test(log_pm_mean_sampling_period ~ missing_var, data = wmt_data)

# Complete case vs missing data comparison
complete_case <- selected_vars %>% 
  na.exclude()

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_pm, sd_pm, median_pm)
missing_summary

missing_data <- selected_vars %>% 
  group_by(home) %>% 
  filter_at(vars(pm_mean_sampling_period:stove_grade_3level), any_vars(is.na(.)))

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_pm, sd_pm, median_pm)
missing_summary

@@

Next, use `mice()` to impute the missing data
Assess imputed data for summary stats and convergence
```{r}
# set seed to be able to replicate imputation
set.seed(123)

# Impute missing data; m = 10 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=10, maxit = 5,
                     method = c("polr", "logreg", "logreg", "logreg", "polr",
                                "polr", "logreg", "logreg", "pmm", "pmm",
                                "pmm", "logreg", "logreg", "polr", "pmm"))
